---
title: "PA1_template.md"
author: "IyaHakky"
date: "Sunday, July 31, 2016"
output: html_document
---

The first Asiisnment for Reprodusible Research course
=======================================================

**The code to load the data**

```{r read_data}
raw.data <- read.csv("activity.csv")
dim(raw.data)
head(raw.data)
```

**What is mean total number of steps taken per day?**
The code to calculate the total number of steps taken per day:

```{r, echo=TRUE}
data.step.count <- aggregate(steps ~ date, data = raw.data, sum)
head(data.step.count)
dim(data.step.count)
mean(data.step.count$step)
median(data.step.count$step)
```

Make a histogram of the total number of steps taken each day
```{r, echo=TRUE}
hist(data.step.count$steps)
```

Now we could calculate mean and medial of step's amount per day
```{r, echo=TRUE}
mean(data.step.count$step)
median(data.step.count$step)
```

**What is the average daily activity pattern?**

A time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r, echo=TRUE}
data.time.series <- aggregate(steps ~ interval, data = raw.data, mean)
dim(data.time.series)
head(data.time.series)

plot(data.time.series, type = "l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r, echo=TRUE}
intervals <-data.time.series$interval
max.steps.interval <- intervals[which.max(data.time.series$steps)]
max.steps.interval
```

**Imputing missing values**

Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r, echo=TRUE}
sum(is.na(raw.data$steps))
```

The strategy for filling all the missing values in the dataset is to use the mean for that 5-minute interval
Firs, let's create a new dataset

```{r, echo=TRUE}
RawDataCorrected <- raw.data
```

The dataset before correction
```{r, echo=TRUE}
dim(RawDataCorrected)
head(RawDataCorrected)
```

Now Let's replace the values

```{r, echo=TRUE}
na.rows <- which(is.na(raw.data$steps))
for (i in na.rows) {
  measurement <- RawDataCorrected[i,]
  intervalNum <- measurement$interval
  rowNumberInAverageStepsPerIntervalSet <- which(data.time.series$interval == intervalNum)
  measurement$steps <- data.time.series[rowNumberInAverageStepsPerIntervalSet,]$steps
  RawDataCorrected[i,] <- measurement
}
```

The dataset After the correction
```{r, echo=TRUE}
dim(RawDataCorrected)
head(RawDataCorrected)
```